Stats

### 2022-03-21 stats/analysis.Rmd
add splithalf analysis on first reliday

```{r splithalfr_hedge}
# fn_score_hedge <- function(ds) {
#   return(mean(abs(ds$clickDistFromTargetCenterX)/160, na.rm = TRUE))
# }
# 
# ### ODD EVEN
# split_scores_hedge_odd_even <- by_split(
#   hedge_intCon_data,
#   hedge_intCon_data$subjID,
#   fn_score_hedge,
#   replications = 1,
#   method = c("odd_even"),
# )
# 
# hedge_odd_even <- split_coefs(split_scores_hedge_odd_even, cor)
# hedge_odd_even_ci  <- split_ci(split_scores_hedge_odd_even, cor)
# 
# save_splithalf <- tibble(hedge_odd_even)
# 
# ### FIRST SECOND
# split_scores_hedge_first_second <- by_split(
#   hedge_intCon_data,
#   hedge_intCon_data$subjID,
#   fn_score_hedge,
#   replications = 1,
#   method = c("first_second"),
# )
# 
# hedge_first_second <- split_coefs(split_scores_hedge_first_second, cor)
# hedge_first_second_ci <- split_ci(split_scores_hedge_first_second, cor)
# 
# save_splithalf <- save_splithalf %>% 
#   mutate(
#     # add confidence interval of coefficients (bca: bias-corrected and accelerated bootstrap confidence intervals)
#     hedge_odd_even_ci_lower = hedge_odd_even_ci$lims["0.025","bca"],
#     hedge_odd_even_ci_upper = hedge_odd_even_ci$lims["0.975","bca"],
#     
#     # same for splitting according to first / second test half
#     hedge_first_second = hedge_first_second, 
#     hedge_first_second_ci_lower = hedge_first_second_ci$lims["0.025","bca"],
#     hedge_first_second_ci_upper = hedge_first_second_ci$lims["0.975","bca"],
#   )
```

@@

```{r box_splithalfr}
# fn_score_box <- function(ds) {
#   return(mean(ds$correctBox, na.rm = TRUE))
# }
# 
# ### ODD EVEN
# split_scores_box_odd_even <- by_split(
#   box_intCon_data,
#   box_intCon_data$subjID,
#   fn_score_box,
#   replications = 1,
#   method = c("odd_even"),
# )
# 
# box_odd_even = split_coefs(split_scores_box_odd_even, cor)
# box_odd_even_ci = split_ci(split_scores_box_odd_even, cor)
#   
# ### FIRST SECOND
# split_scores_box_first_second <- by_split(
#   box_intCon_data,
#   box_intCon_data$subjID,
#   fn_score_box,
#   replications = 1,
#   method = c("first_second"),
# )
# 
# box_first_second = split_coefs(split_scores_box_first_second, cor)
# box_first_second_ci = split_ci(split_scores_box_first_second, cor)
# 
# save_splithalf <- save_splithalf %>% 
#   mutate(
#     # add splitting according to odd / even test half
#     box_odd_even = box_odd_even, 
#     box_odd_even_ci_lower = box_odd_even_ci$lims["0.025","bca"],
#     box_odd_even_ci_upper = box_odd_even_ci$lims["0.975","bca"],
#     
#     # same for splitting according to first / second test half
#     box_first_second = box_first_second, 
#     box_first_second_ci_lower = box_first_second_ci$lims["0.025","bca"],
#     box_first_second_ci_upper = box_first_second_ci$lims["0.975","bca"],
#   )
```

```{r save_splithalfr}
# save_splithalf
# 
# write.csv(save_splithalf, "gafo-splithalf.csv", quote = F, row.names = F)
# saveRDS(save_splithalf, file = "gafo-splithalf.rds")
```

>>>>

@@

```{r splithalfr_hedge_kids}
fn_score_hedge <- function(ds) {
  return(mean(abs(ds$clickDistFromTargetCenterX)/160, na.rm = TRUE))
}

hedge_intCon_data <- reli %>% 
  filter(studyversion == "hedge" & reliday == "reliday1") %>% 
  mutate(
    # summarize bins, so that 9 + 10 = bin 5
    # bin = ceiling(as.numeric(targetPosition)/2)

    # summarize so that 1 + 10 = bin 5
    symmetricBin = case_when(targetPosition == "5" | targetPosition == "6" ~ 1, 
                             targetPosition == "4" | targetPosition == "7" ~ 2,
                             targetPosition == "3" | targetPosition == "8" ~ 3, 
                             targetPosition == "2" | targetPosition == "9" ~ 4,
                             targetPosition == "1" | targetPosition == "10"~ 5, 
                       )
  )

# random split
splitscores_hedge_random_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  replications = 1,
  method = c("random"),
  replace = TRUE,
  split_p = 1,
)

hedge_random_kids <- split_coefs(splitscores_hedge_random_kids, cor)
hedge_random_kids_ci  <- split_ci(splitscores_hedge_random_kids, cor)

# create dataframe to save data
splithalf_data <- tibble(
                    studyversion = "hedge", 
                    sample = "kids", 
                    split = "random", 
                    stratification = "none", 
                    mean = hedge_random_kids, 
                    CI_lower = hedge_random_kids_ci$lims["0.025","bca"], 
                    CI_upper = hedge_random_kids_ci$lims["0.975","bca"])

# random split with stratification by target position
splitscores_hedge_randomStrat_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricBin),
  replications = 1,
  method = c("random"),
  replace = TRUE,
  split_p = 1,
)

hedge_randomStrat_kids <- split_coefs(splitscores_hedge_randomStrat_kids, cor)
hedge_randomStrat_kids_ci <- split_ci(splitscores_hedge_randomStrat_kids, cor)

splithalf_data <- splithalf_data %>% add_row(
                                        studyversion = "hedge", 
                                        sample = "kids", 
                                        split = "random",
                                        stratification = "target position",
                                        mean = hedge_randomStrat_kids, 
                                        CI_lower = hedge_randomStrat_kids_ci$lims["0.025","bca"], 
                                        CI_upper = hedge_randomStrat_kids_ci$lims["0.975","bca"]
                                      )

# odd even split
splitscores_hedge_oddeven_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  replications = 1,
  method = c("odd_even"),
)

hedge_oddeven_kids <- split_coefs(splitscores_hedge_oddeven_kids, cor)
hedge_oddeven_kids_ci  <- split_ci(splitscores_hedge_oddeven_kids, cor)

splithalf_data <- splithalf_data %>% add_row(
                                        studyversion = "hedge", 
                                        sample = "kids", 
                                        split = "odd even", 
                                        stratification = "none", 
                                        mean = hedge_oddeven_kids, 
                                        CI_lower = hedge_oddeven_kids_ci$lims["0.025","bca"], 
                                        CI_upper = hedge_oddeven_kids_ci$lims["0.975","bca"]
                                      )

# odd even split with stratification by target position
splitscores_hedge_oddevenStrat_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricBin),
  replications = 1,
  method = c("odd_even"),
)

hedge_oddevenStrat_kids <- split_coefs(splitscores_hedge_oddevenStrat_kids, cor)
hedge_oddevenStrat_kids_ci <- split_ci(splitscores_hedge_oddevenStrat_kids, cor)

splithalf_data <- splithalf_data %>% add_row(
                                        studyversion = "hedge", 
                                        sample = "kids", 
                                        split = "odd even",
                                        stratification = "target position",
                                        mean = hedge_oddevenStrat_kids, 
                                        CI_lower = hedge_oddevenStrat_kids_ci$lims["0.025","bca"], 
                                        CI_upper = hedge_oddevenStrat_kids_ci$lims["0.975","bca"]
                                      )

# first second testhalves split
splitscores_hedge_firstsecond_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  replications = 1,
  method = c("first_second"),
)

hedge_firstsecond_kids <- split_coefs(splitscores_hedge_firstsecond_kids, cor)
hedge_firstsecond_kids_ci <- split_ci(splitscores_hedge_firstsecond_kids, cor)

splithalf_data <- splithalf_data %>% add_row(
                                        studyversion = "hedge", 
                                        sample = "kids", 
                                        split = "first second", 
                                        stratification = "none",                                        
                                        mean = hedge_firstsecond_kids, 
                                        CI_lower = hedge_firstsecond_kids_ci$lims["0.025","bca"], 
                                        CI_upper = hedge_firstsecond_kids_ci$lims["0.975","bca"]
                                      )

# first second testhalves split with stratification by target position
splitscores_hedge_firstsecondStrat_kids <- by_split(
  hedge_intCon_data %>% filter(sample == "kids"),
  hedge_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_hedge,
  stratification = hedge_intCon_data %>% filter(sample == "kids") %>% pull(symmetricBin),
  replications = 1,
  method = c("odd_even"),
)

hedge_firstsecondStrat_kids <- split_coefs(splitscores_hedge_firstsecondStrat_kids, cor)
hedge_firstsecondStrat_kids_ci <- split_ci(splitscores_hedge_firstsecondStrat_kids, cor)

splithalf_data <- splithalf_data %>% add_row(
                                        studyversion = "hedge", 
                                        sample = "kids", 
                                        split = "first second",
                                        stratification = "target position",
                                        mean = hedge_firstsecondStrat_kids, 
                                        CI_lower = hedge_firstsecondStrat_kids_ci$lims["0.025","bca"], 
                                        CI_upper = hedge_firstsecondStrat_kids_ci$lims["0.975","bca"]
                                      )
```

```{r splithalfr_hedge_adults}
# random split
splitscores_hedge_random_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  replications = 1,
  method = c("random"),
  replace = TRUE,
  split_p = 1,
)

hedge_random_adults <- split_coefs(splitscores_hedge_random_adults, cor)
hedge_random_adults_ci  <- split_ci(splitscores_hedge_random_adults, cor)

splithalf_data <- splithalf_data %>% add_row(
                                        studyversion = "hedge", 
                                        sample = "adults", 
                                        split = "random", 
                                        stratification = "none", 
                                        mean = hedge_random_adults, 
                                        CI_lower = hedge_random_adults_ci$lims["0.025","bca"], 
                                        CI_upper = hedge_random_adults_ci$lims["0.975","bca"]
                                      )

# random split with stratification by target position
splitscores_hedge_randomStrat_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricBin),
  replications = 1,
  method = c("random"),
  replace = TRUE,
  split_p = 1,
)

hedge_randomStrat_adults <- split_coefs(splitscores_hedge_randomStrat_adults, cor)
hedge_randomStrat_adults_ci <- split_ci(splitscores_hedge_randomStrat_adults, cor)

splithalf_data <- splithalf_data %>% add_row(
                                        studyversion = "hedge", 
                                        sample = "adults", 
                                        split = "random",
                                        stratification = "target position",
                                        mean = hedge_randomStrat_adults, 
                                        CI_lower = hedge_randomStrat_adults_ci$lims["0.025","bca"], 
                                        CI_upper = hedge_randomStrat_adults_ci$lims["0.975","bca"]
                                      )

# odd even split
splitscores_hedge_oddeven_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  replications = 1,
  method = c("odd_even"),
)

hedge_oddeven_adults <- split_coefs(splitscores_hedge_oddeven_adults, cor)
hedge_oddeven_adults_ci  <- split_ci(splitscores_hedge_oddeven_adults, cor)

splithalf_data <- splithalf_data %>% add_row(
                                        studyversion = "hedge", 
                                        sample = "adults", 
                                        split = "odd even", 
                                        stratification = "none", 
                                        mean = hedge_oddeven_adults, 
                                        CI_lower = hedge_oddeven_adults_ci$lims["0.025","bca"], 
                                        CI_upper = hedge_oddeven_adults_ci$lims["0.975","bca"]
                                      )

# odd even split with stratification by target position
splitscores_hedge_oddevenStrat_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricBin),
  replications = 1,
  method = c("odd_even"),
)

hedge_oddevenStrat_adults <- split_coefs(splitscores_hedge_oddevenStrat_adults, cor)
hedge_oddevenStrat_adults_ci <- split_ci(splitscores_hedge_oddevenStrat_adults, cor)

splithalf_data <- splithalf_data %>% add_row(
                                        studyversion = "hedge", 
                                        sample = "adults", 
                                        split = "odd even",
                                        stratification = "target position",
                                        mean = hedge_oddevenStrat_adults, 
                                        CI_lower = hedge_oddevenStrat_adults_ci$lims["0.025","bca"], 
                                        CI_upper = hedge_oddevenStrat_adults_ci$lims["0.975","bca"]
                                      )

# first second testhalves split
splitscores_hedge_firstsecond_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  replications = 1,
  method = c("first_second"),
)

hedge_firstsecond_adults <- split_coefs(splitscores_hedge_firstsecond_adults, cor)
hedge_firstsecond_adults_ci <- split_ci(splitscores_hedge_firstsecond_adults, cor)

splithalf_data <- splithalf_data %>% add_row(
                                        studyversion = "hedge", 
                                        sample = "adults", 
                                        split = "first second", 
                                        stratification = "none",                                        
                                        mean = hedge_firstsecond_adults, 
                                        CI_lower = hedge_firstsecond_adults_ci$lims["0.025","bca"], 
                                        CI_upper = hedge_firstsecond_adults_ci$lims["0.975","bca"]
                                      )

# first second testhalves split with stratification by target position
splitscores_hedge_firstsecondStrat_adults <- by_split(
  hedge_intCon_data %>% filter(sample == "adults"),
  hedge_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_hedge,
  stratification = hedge_intCon_data %>% filter(sample == "adults") %>% pull(symmetricBin),
  replications = 1,
  method = c("odd_even"),
)

hedge_firstsecondStrat_adults <- split_coefs(splitscores_hedge_firstsecondStrat_adults, cor)
hedge_firstsecondStrat_adults_ci <- split_ci(splitscores_hedge_firstsecondStrat_adults, cor)

splithalf_data <- splithalf_data %>% add_row(
                                        studyversion = "hedge", 
                                        sample = "adults", 
                                        split = "first second",
                                        stratification = "target position",
                                        mean = hedge_firstsecondStrat_adults, 
                                        CI_lower = hedge_firstsecondStrat_adults_ci$lims["0.025","bca"], 
                                        CI_upper = hedge_firstsecondStrat_adults_ci$lims["0.975","bca"]
                                      )
```

```{r splithalfr_box_kids}
fn_score_box <- function(ds) {
  return(mean(ds$correctBox, na.rm = TRUE))
}

box_intCon_data <- reli %>% 
  filter(studyversion == "box" & reliday == "reliday1")

box_intCon_data %>% 
  group_by(subjID, targetPosition) %>% 
  summarise(n = n()) %>% 
  filter(n < 2)

# random split
splitscores_box_random_kids <- by_split(
  box_intCon_data %>% filter(sample == "kids"),
  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_box,
  replications = 1,
  method = c("random"),
  replace = TRUE,
  split_p = 1,
)

box_random_kids <- split_coefs(splitscores_box_random_kids, cor)
box_random_kids_ci  <- split_ci(splitscores_box_random_kids, cor)

# create dataframe to save data
splithalf_data <- splithalf_data %>% add_row(
                                        studyversion = "box", 
                                        sample = "kids", 
                                        split = "random", 
                                        stratification = "none", 
                                        mean = box_random_kids, 
                                        CI_lower = box_random_kids_ci$lims["0.025","bca"], 
                                        CI_upper = box_random_kids_ci$lims["0.975","bca"])

# random split with stratification by target position
splitscores_box_randomStrat_kids <- by_split(
  box_intCon_data %>% filter(sample == "kids"),
  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_box,
  stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(targetPosition),
  replications = 1,
  method = c("random"),
  replace = TRUE,
  split_p = 1,
  careful = FALSE, 
)

box_randomStrat_kids <- split_coefs(splitscores_box_randomStrat_kids, cor)
box_randomStrat_kids_ci <- split_ci(splitscores_box_randomStrat_kids, cor)

splithalf_data <- splithalf_data %>% add_row(
                                        studyversion = "box", 
                                        sample = "kids", 
                                        split = "random",
                                        stratification = "target position",
                                        mean = box_randomStrat_kids, 
                                        CI_lower = box_randomStrat_kids_ci$lims["0.025","bca"], 
                                        CI_upper = box_randomStrat_kids_ci$lims["0.975","bca"]
                                      )

# odd even split
splitscores_box_oddeven_kids <- by_split(
  box_intCon_data %>% filter(sample == "kids"),
  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_box,
  replications = 1,
  method = c("odd_even"),
)

box_oddeven_kids <- split_coefs(splitscores_box_oddeven_kids, cor)
box_oddeven_kids_ci  <- split_ci(splitscores_box_oddeven_kids, cor)

splithalf_data <- splithalf_data %>% add_row(
                                        studyversion = "box", 
                                        sample = "kids", 
                                        split = "odd even", 
                                        stratification = "none", 
                                        mean = box_oddeven_kids, 
                                        CI_lower = box_oddeven_kids_ci$lims["0.025","bca"], 
                                        CI_upper = box_oddeven_kids_ci$lims["0.975","bca"]
                                      )

# odd even split with stratification by target position
splitscores_box_oddevenStrat_kids <- by_split(
  box_intCon_data %>% filter(sample == "kids"),
  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_box,
  stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(targetPosition),
  replications = 1,
  method = c("odd_even"),
  careful = FALSE
)

box_oddevenStrat_kids <- split_coefs(splitscores_box_oddevenStrat_kids, cor)
box_oddevenStrat_kids_ci <- split_ci(splitscores_box_oddevenStrat_kids, cor)

splithalf_data <- splithalf_data %>% add_row(
                                        studyversion = "box", 
                                        sample = "kids", 
                                        split = "odd even",
                                        stratification = "target position",
                                        mean = box_oddevenStrat_kids, 
                                        CI_lower = box_oddevenStrat_kids_ci$lims["0.025","bca"], 
                                        CI_upper = box_oddevenStrat_kids_ci$lims["0.975","bca"]
                                      )

# first second testhalves split
splitscores_box_firstsecond_kids <- by_split(
  box_intCon_data %>% filter(sample == "kids"),
  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_box,
  replications = 1,
  method = c("first_second"),
)

box_firstsecond_kids <- split_coefs(splitscores_box_firstsecond_kids, cor)
box_firstsecond_kids_ci <- split_ci(splitscores_box_firstsecond_kids, cor)

splithalf_data <- splithalf_data %>% add_row(
                                        studyversion = "box", 
                                        sample = "kids", 
                                        split = "first second", 
                                        stratification = "none",                                        
                                        mean = box_firstsecond_kids, 
                                        CI_lower = box_firstsecond_kids_ci$lims["0.025","bca"], 
                                        CI_upper = box_firstsecond_kids_ci$lims["0.975","bca"]
                                      )

# first second testhalves split with stratification by target position
splitscores_box_firstsecondStrat_kids <- by_split(
  box_intCon_data %>% filter(sample == "kids"),
  box_intCon_data %>% filter(sample == "kids") %>% pull(subjID),
  fn_score_box,
  stratification = box_intCon_data %>% filter(sample == "kids") %>% pull(targetPosition),
  replications = 1,
  method = c("odd_even"),
  careful = FALSE,
)

box_firstsecondStrat_kids <- split_coefs(splitscores_box_firstsecondStrat_kids, cor)
box_firstsecondStrat_kids_ci <- split_ci(splitscores_box_firstsecondStrat_kids, cor)

splithalf_data <- splithalf_data %>% add_row(
                                        studyversion = "box", 
                                        sample = "kids", 
                                        split = "first second",
                                        stratification = "target position",
                                        mean = box_firstsecondStrat_kids, 
                                        CI_lower = box_firstsecondStrat_kids_ci$lims["0.025","bca"], 
                                        CI_upper = box_firstsecondStrat_kids_ci$lims["0.975","bca"]
                                      )
```

```{r splithalfr_box_adults}
# random split
splitscores_box_random_adults <- by_split(
  box_intCon_data %>% filter(sample == "adults"),
  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_box,
  replications = 1,
  method = c("random"),
  replace = TRUE,
  split_p = 1,
)

box_random_adults <- split_coefs(splitscores_box_random_adults, cor)
box_random_adults_ci  <- split_ci(splitscores_box_random_adults, cor)

# create dataframe to save data
splithalf_data <- splithalf_data %>% add_row(
                                        studyversion = "box", 
                                        sample = "adults", 
                                        split = "random", 
                                        stratification = "none", 
                                        mean = box_random_adults, 
                                        CI_lower = box_random_adults_ci$lims["0.025","bca"], 
                                        CI_upper = box_random_adults_ci$lims["0.975","bca"]
                                      )

# random split with stratification by target position
splitscores_box_randomStrat_adults <- by_split(
  box_intCon_data %>% filter(sample == "adults"),
  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_box,
  stratification = box_intCon_data %>% filter(sample == "adults") %>% pull(targetPosition),
  replications = 1,
  method = c("random"),
  replace = TRUE,
  split_p = 1,
  careful = FALSE,
)

box_randomStrat_adults <- split_coefs(splitscores_box_randomStrat_adults, cor)
box_randomStrat_adults_ci <- split_ci(splitscores_box_randomStrat_adults, cor)

splithalf_data <- splithalf_data %>% add_row(
                                        studyversion = "box", 
                                        sample = "adults", 
                                        split = "random",
                                        stratification = "target position",
                                        mean = box_randomStrat_adults, 
                                        CI_lower = box_randomStrat_adults_ci$lims["0.025","bca"], 
                                        CI_upper = box_randomStrat_adults_ci$lims["0.975","bca"]
                                      )

# odd even split
splitscores_box_oddeven_adults <- by_split(
  box_intCon_data %>% filter(sample == "adults"),
  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_box,
  replications = 1,
  method = c("odd_even"),
)

box_oddeven_adults <- split_coefs(splitscores_box_oddeven_adults, cor)
box_oddeven_adults_ci  <- split_ci(splitscores_box_oddeven_adults, cor)

splithalf_data <- splithalf_data %>% add_row(
                                        studyversion = "box", 
                                        sample = "adults", 
                                        split = "odd even", 
                                        stratification = "none", 
                                        mean = box_oddeven_adults, 
                                        CI_lower = box_oddeven_adults_ci$lims["0.025","bca"], 
                                        CI_upper = box_oddeven_adults_ci$lims["0.975","bca"]
                                      )

# odd even split with stratification by target position
splitscores_box_oddevenStrat_adults <- by_split(
  box_intCon_data %>% filter(sample == "adults"),
  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_box,
  stratification = box_intCon_data %>% filter(sample == "adults") %>% pull(targetPosition),
  replications = 1,
  method = c("odd_even"),
  careful = FALSE,
)

box_oddevenStrat_adults <- split_coefs(splitscores_box_oddevenStrat_adults, cor)
box_oddevenStrat_adults_ci <- split_ci(splitscores_box_oddevenStrat_adults, cor)

splithalf_data <- splithalf_data %>% add_row(
                                        studyversion = "box", 
                                        sample = "adults", 
                                        split = "odd even",
                                        stratification = "target position",
                                        mean = box_oddevenStrat_adults, 
                                        CI_lower = box_oddevenStrat_adults_ci$lims["0.025","bca"], 
                                        CI_upper = box_oddevenStrat_adults_ci$lims["0.975","bca"]
                                      )

# first second testhalves split
splitscores_box_firstsecond_adults <- by_split(
  box_intCon_data %>% filter(sample == "adults"),
  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_box,
  replications = 1,
  method = c("first_second"),
)

box_firstsecond_adults <- split_coefs(splitscores_box_firstsecond_adults, cor)
box_firstsecond_adults_ci <- split_ci(splitscores_box_firstsecond_adults, cor)

splithalf_data <- splithalf_data %>% add_row(
                                        studyversion = "box", 
                                        sample = "adults", 
                                        split = "first second", 
                                        stratification = "none",                                        
                                        mean = box_firstsecond_adults, 
                                        CI_lower = box_firstsecond_adults_ci$lims["0.025","bca"], 
                                        CI_upper = box_firstsecond_adults_ci$lims["0.975","bca"]
                                      )

# first second testhalves split with stratification by target position
splitscores_box_firstsecondStrat_adults <- by_split(
  box_intCon_data %>% filter(sample == "adults"),
  box_intCon_data %>% filter(sample == "adults") %>% pull(subjID),
  fn_score_box,
  stratification = box_intCon_data %>% filter(sample == "adults") %>% pull(targetPosition),
  replications = 1,
  method = c("odd_even"),
  careful = FALSE,
)

box_firstsecondStrat_adults <- split_coefs(splitscores_box_firstsecondStrat_adults, cor)
box_firstsecondStrat_adults_ci <- split_ci(splitscores_box_firstsecondStrat_adults, cor)

splithalf_data <- splithalf_data %>% add_row(
                                        studyversion = "box", 
                                        sample = "adults", 
                                        split = "first second",
                                        stratification = "target position",
                                        mean = box_firstsecondStrat_adults, 
                                        CI_lower = box_firstsecondStrat_adults_ci$lims["0.025","bca"], 
                                        CI_upper = box_firstsecondStrat_adults_ci$lims["0.975","bca"]
                                      )
```

```{r splithalf_plot}
splithalf_data %>% 
  mutate(sample = fct_rev(sample)) %>%
  unite("samplegroup", c(studyversion, sample), sep = " - ", remove = FALSE) %>% 
  mutate(samplegroup = fct_rev(samplegroup)) %>%
  unite("method", c(split, stratification), sep = ", ", remove = FALSE) %>% 
  ggplot(aes(x = method, y = mean, color = sample, group = studyversion)) + 
    geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper), colour = "black", width = .1, position = position_dodge(0.1)) +
    geom_point(position = position_dodge(0.1), size = 3) +
    scale_y_continuous(limits = c(0, 1), breaks = seq(0, 1, 0.2)) +
    scale_color_manual(values = c("#006c66", "darkgrey"), guide = "none") +
    labs(x = "Splitting & stratification method", y = "") +
    coord_flip() + 
    facet_wrap(~ samplegroup) + 
    theme(legend.position = "none", panel.spacing = unit(1.5, "lines"))

ggsave("../figures/gafo_splithalf.png", width = 6, height = 4, scale = 1.4)
```

```{r splithalf_table}
knitr::kable(splithalf_data)
```

```{r save_splithalf_data}
write.csv(splithalf_data, "gafo-splithalf.csv", quote = F, row.names = F)
saveRDS(splithalf_data, file = "gafo-splithalf.rds")
```
